Design and implementaiton of a live coding environment for data science

### 2017-11-06 live/paper.tex
Properties section

\usepackage{lineno,hyperref,xcolor}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{xypic}
\usepackage{semantic}
\usepackage{booktabs} 
\usepackage{subcaption}
\usepackage{enumitem}
\setlist{leftmargin=6mm}

@@

\begin{figure*}[t]
\vspace{-0.5em}
\begin{equation*}
\begin{array}{ll}
\ident{bind}_{\Gamma, \Delta}(e_0.m(e_1, \ldots, e_n)) = &(1)~~\\ 
\qquad \bndclr{v}, (\{\bndclr{v}\} \cup V_0 \cup \ldots \cup V_n, E \cup E_0 \cup \ldots \cup E_n)\\
\quad \textnormal{when}~\bndclr{v_i}, (V_i, E_i) = \ident{bind}_{\Gamma, \Delta}(e_i)\\
\quad \textnormal{and}~\bndclr{v} = \Delta(\bknd{mem}(m),[(\bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v_n}, \blbl{arg}(n))])\\
\quad \textnormal{let}~E = \{ (\bndclr{v}, \bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v}, \bndclr{v_n}, \blbl{arg}(n))\}
\\[0.75em]
\ident{bind}_{\Gamma, \Delta}(e_0.m(e_1, \ldots, e_n)) = &(2)\\ 
\qquad \bndclr{v}, (\{\bndclr{v}\} \cup V_0 \cup \ldots \cup V_n, E \cup E_0 \cup \ldots \cup E_n)\\
\quad \textnormal{when}~\bndclr{v_i}, (V_i, E_i) = \ident{bind}_{\Gamma, \Delta}(e_i)\\
\quad \textnormal{and}~(\bknd{mem}(m),[(\bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v_n}, \blbl{arg}(n))]) \notin \ident{dom}(\Delta)\hspace{-200em}.\\
\quad \textnormal{let}~\bndclr{v} = \bnd{mem}(m, s), s~\textnormal{fresh}\\
\quad \textnormal{let}~E = \{ (\bndclr{v}, \bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v},\bndclr{v_n}, \blbl{arg}(n)) \}
\\[0.75em]
\ident{bind}_{\Gamma, \Delta}(\kvd{let}~x=e_1~\kvd{in}~e_2) = \bndclr{v}, (\{\bndclr{v}\} \cup V \cup V_1, E \cup E_1)&(3)\\
\quad \textnormal{let}~\bndclr{v_1}, (V_1,E_1) = \ident{bind}_{\Gamma,\Delta}(e_1)\\
\quad \textnormal{let}~\Gamma_1 = \Gamma \cup \{(x,\bndclr{v_1})\} \\
\quad \textnormal{let}~\bndclr{v}, (V, E) = \ident{bind}_{\Gamma_1, \Delta}(e_2)
\end{array}
\begin{array}{ll}
\ident{bind}_{\Gamma, \Delta}(n) = \bnd{val}(n), (\{ \bnd{val}(n) \}, \emptyset) }&(4)
\\[0.75em]
\ident{bind}_{\Gamma, \Delta}(x) = \bndclr{v}, (\{ \bndclr{v} \}, \emptyset)\quad \textnormal{when}~\bndclr{v} = \Gamma(x)&(6)
\\[1em]
\ident{bind}_{\Gamma, \Delta}(\lambda x \rightarrow e) = \bndclr{v}, (\{\bndclr{v}\} \cup V, \{e\} \cup E)&(7)\\
\quad \textnormal{when}~\Gamma_1 = \Gamma \cup \{ x, \bnd{var}(x) \}\\
\quad \textnormal{and}~\bndclr{v_0}, (V, E) = \ident{bind}_{\Gamma_1, \Delta}(e)\\
\quad \textnormal{and}~\bndclr{v} = \Delta(\bknd{fun}(x),[(\bndclr{v_0}, \blbl{body})])\\
\quad \textnormal{let}~e = (\bndclr{v}, \bndclr{v_0}, \blbl{body}) 
\\[1em]
\ident{bind}_{\Gamma, \Delta}(\lambda x \rightarrow e) = \bndclr{v}, (\{\bndclr{v}\} \cup V, \{e\} \cup E)&(8)\\
\quad \textnormal{when}~\Gamma_1 = \Gamma \cup \{ x, \bnd{var}(x) \}\\
\quad \textnormal{and}~\bndclr{v_0}, (V, E) = \ident{bind}_{\Gamma_1, \Delta}(e)\\
\quad \textnormal{and}~(\bknd{fun}(x),[(\bndclr{v_0}, \blbl{body})])\notin \ident{dom}(\Delta)\\
\quad \textnormal{let}~\bndclr{v} = \bnd{fun}(s, x), s~\textnormal{fresh}\\
\quad \textnormal{let}~e = (\bndclr{v},\bndclr{v_0},\blbl{body}) 
\\[0.5em]
\end{array}
\end{equation*}
\vspace{-0.5em}
\caption{Rules of the binding process, which constructs a dependency graph for an expression.}
\label{fig:binding-rules}
\end{figure*}

@@

\begin{figure}[!b]
\vspace{-0.5em}
\begin{equation*}
\begin{array}{l}
\Delta_{i}(\bknd{mem}(m), [(\bndclr{v_0},\blbl{arg}(0)),\ldots, (\bndclr{v_n},\blbl{arg}(n))]) = \bndclr{v}\\
\quad \textnormal{for all}~\bnd{mem}(m, s) \in V\\
\quad \textnormal{such that}~(\bnd{mem}(m, s), \bndclr{v_i}, \blbl{arg}(i)) \in E~\textnormal{for}~i\in 0,..,n
\\[0.75em]
\Delta_{i}(\bknd{fun}(x), [(\bndclr{v_1},\blbl{body})]) = \bndclr{v}\\
\quad \textnormal{for all}~\bnd{fun}(x, s) \in V\\
\quad \textnormal{such that}~(\bnd{fun}(x, s), \bndclr{v_1}, \blbl{body}) \in E
\\[0.75em]
\Delta_{i}(\bkndclr{v}) = \Delta_{i-1}(\bkndclr{v})\quad \textnormal{(otherwise)}
\end{array}
\end{equation*}
\vspace{-0.5em}
\caption{Updating the node cache after binding a new graph}
\label{fig:loop}
\end{figure}

@@

\newpage
\section{Properties}
\label{sec:properties}

\subsection{Host language}

@@

@@

\item 
Compositionality, i.e. if $e \rightsquigarrow e'$ and $C[e] \rightsquigarrow e''$ then also
  $C[e'] \rightsquigarrow e''$.
\end{itemize}
\end{definition}

@@

@@

\begin{lem}[Let-free correctness]
Given an expression $e$ that has no free variables and does not contain let bindnigs, together with
a lookup table $\Delta$ obtained from any sequence of expressions according to Figure~\ref{fig:loop}, 
let $\bndclr{v}, (V, E) = \ident{bind}_{\emptyset, \Delta}(e)$. If $\bndclr{v}\Downarrow d$ 
over a graph $(V, E)$ then $d = p$ for some $p$ and $e \rightsquigarrow p$.
\end{lem}
\begin{proof}
Every dependency graph node $\bndclr{v}$ corresponds to an expression $e$ with free variables
$FV(e)$. We obtain preview $\bndclr{v}\Downarrow d$ such that if $FV(e) = \emptyset$ then
$d = p$ for some $p$, otherwise, $d = \llbracket e' \rrbracket_{FV(e)}$.  
We show that either $e \rightsquigarrow p$ or that for any $C$ such that $FV(C[e]) = \emptyset$
it holds that $C[e] \rightsquigarrow e''$ and $C[e'] \rightsquigarrow e''$.
By induction over the structure of the evaluation:

\vspace{0.5em}\noindent\emph{(val)} $\bnd{val}(n) \Downarrow n$ and so $p=n$. The only
  \ident{bind} case that generates $\bnd{val}(n)$ in the absence of let bindings is~(4) and
  so $e = n$.

\vspace{0.5em}\noindent\emph{(mem-val)} $\bnd{mem}(m, s) \Downarrow p$. By induction, there
  are nodes $\bndclr{v_i}$ representing expressions $e_i$ and previews $\bndclr{v_i}\Downarrow p_i$
  such that $e_i \rightsquigarrow p_i$. The only \ident{bind} case that generates the $\bnd{mem}(m, s)$
  node in the absence of let binding is~(2) and so $e=e_0.m(e_1, \ldots, e_n)$. From 
  (\emph{mem-val}), $p_0.m(p_1, \ldots, p_n) \rightsquigarrow p$ and from the compositionality 
  of $\rightsquigarrow$, it is the case that $e \rightsquigarrow p$.

\end{proof}

\begin{theorem}[Correctness]
(Same as let-free version, but using let elimination to say that this works for any expression)
\end{theorem}

@@

>>>>

\usepackage{lineno,hyperref,xcolor}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{xypic}
\usepackage{semantic}
\usepackage{booktabs} 
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage[shortlabels]{enumerate}
\setlist{leftmargin=6mm}

@@

\begin{figure*}[t]
\vspace{-0.5em}
\begin{equation*}
\begin{array}{ll}
\ident{bind}_{\Gamma, \Delta}(e_0.m(e_1, \ldots, e_n)) = &(1)~~\\ 
\qquad \bndclr{v}, (\{\bndclr{v}\} \cup V_0 \cup \ldots \cup V_n, E \cup E_0 \cup \ldots \cup E_n)\\
\quad \textnormal{when}~\bndclr{v_i}, (V_i, E_i) = \ident{bind}_{\Gamma, \Delta}(e_i)\\
\quad \textnormal{and}~\bndclr{v} = \Delta(\bknd{mem}(m),[(\bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v_n}, \blbl{arg}(n))])\\
\quad \textnormal{let}~E = \{ (\bndclr{v}, \bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v}, \bndclr{v_n}, \blbl{arg}(n))\}
\\[0.75em]
\ident{bind}_{\Gamma, \Delta}(e_0.m(e_1, \ldots, e_n)) = &(2)\\ 
\qquad \bndclr{v}, (\{\bndclr{v}\} \cup V_0 \cup \ldots \cup V_n, E \cup E_0 \cup \ldots \cup E_n)\\
\quad \textnormal{when}~\bndclr{v_i}, (V_i, E_i) = \ident{bind}_{\Gamma, \Delta}(e_i)\\
\quad \textnormal{and}~(\bknd{mem}(m),[(\bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v_n}, \blbl{arg}(n))]) \notin \ident{dom}(\Delta)\hspace{-200em}.\\
\quad \textnormal{let}~\bndclr{v} = \bnd{mem}(m, s), s~\textnormal{fresh}\\
\quad \textnormal{let}~E = \{ (\bndclr{v}, \bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v},\bndclr{v_n}, \blbl{arg}(n)) \}
\\[0.75em]
\ident{bind}_{\Gamma, \Delta}(\kvd{let}~x=e_1~\kvd{in}~e_2) = \bndclr{v}, (\{\bndclr{v}\} \cup V \cup V_1, E \cup E_1)&(3)\\
\quad \textnormal{let}~\bndclr{v_1}, (V_1,E_1) = \ident{bind}_{\Gamma,\Delta}(e_1)\\
\quad \textnormal{let}~\Gamma_1 = \Gamma \cup \{(x,\bndclr{v_1})\} \\
\quad \textnormal{let}~\bndclr{v}, (V, E) = \ident{bind}_{\Gamma_1, \Delta}(e_2)
\end{array}
\begin{array}{ll}
\ident{bind}_{\Gamma, \Delta}(n) = \bnd{val}(n), (\{ \bnd{val}(n) \}, \emptyset) }&(4)
\\[0.75em]
\ident{bind}_{\Gamma, \Delta}(x) = \bndclr{v}, (\{ \bndclr{v} \}, \emptyset)\quad \textnormal{when}~\bndclr{v} = \Gamma(x)&(5)
\\[1em]
\ident{bind}_{\Gamma, \Delta}(\lambda x \rightarrow e) = \bndclr{v}, (\{\bndclr{v}\} \cup V, \{e\} \cup E)&(6)\\
\quad \textnormal{when}~\Gamma_1 = \Gamma \cup \{ x, \bnd{var}(x) \}\\
\quad \textnormal{and}~\bndclr{v_0}, (V, E) = \ident{bind}_{\Gamma_1, \Delta}(e)\\
\quad \textnormal{and}~\bndclr{v} = \Delta(\bknd{fun}(x),[(\bndclr{v_0}, \blbl{body})])\\
\quad \textnormal{let}~e = (\bndclr{v}, \bndclr{v_0}, \blbl{body}) 
\\[1em]
\ident{bind}_{\Gamma, \Delta}(\lambda x \rightarrow e) = \bndclr{v}, (\{\bndclr{v}\} \cup V, \{e\} \cup E)&(7)\\
\quad \textnormal{when}~\Gamma_1 = \Gamma \cup \{ x, \bnd{var}(x) \}\\
\quad \textnormal{and}~\bndclr{v_0}, (V, E) = \ident{bind}_{\Gamma_1, \Delta}(e)\\
\quad \textnormal{and}~(\bknd{fun}(x),[(\bndclr{v_0}, \blbl{body})])\notin \ident{dom}(\Delta)\\
\quad \textnormal{let}~\bndclr{v} = \bnd{fun}(s, x), s~\textnormal{fresh}\\
\quad \textnormal{let}~e = (\bndclr{v},\bndclr{v_0},\blbl{body}) 
\\[0.5em]
\end{array}
\end{equation*}
\vspace{-0.5em}
\caption{Rules of the binding process, which constructs a dependency graph for an expression.}
\label{fig:binding-rules}
\end{figure*}

@@

\begin{figure}[!b]
\vspace{-0.5em}
\begin{equation*}
\begin{array}{l}
\Delta_{i}(\bknd{mem}(m), [(\bndclr{v_0},\blbl{arg}(0)),\ldots, (\bndclr{v_n},\blbl{arg}(n))]) = \bnd{mem}(m, s)\\
\quad \textnormal{for all}~\bnd{mem}(m, s) \in V\\
\quad \textnormal{such that}~(\bnd{mem}(m, s), \bndclr{v_i}, \blbl{arg}(i)) \in E~\textnormal{for}~i\in 0,..,n
\\[0.75em]
\Delta_{i}(\bknd{fun}(x), [(\bndclr{v_1},\blbl{body})]) = \bnd{fun}(x, s)\\
\quad \textnormal{for all}~\bnd{fun}(x, s) \in V\\
\quad \textnormal{such that}~(\bnd{fun}(x, s), \bndclr{v_1}, \blbl{body}) \in E
\\[0.75em]
\Delta_{i}(\bkndclr{v}) = \Delta_{i-1}(\bkndclr{v})\quad \textnormal{(otherwise)}
\end{array}
\end{equation*}
\vspace{-0.5em}
\caption{Updating the node cache after binding a new graph}
\label{fig:loop}
\end{figure}

@@

\newpage
\section{Properties of preview evaluation}
\label{sec:properties}

The dependency graph makes it possible to cache partial results when evaluating previews. 
The construction of dependency graphs and evaluation of previews needs to have two main properties.
First, if we evaluate a preview using dependency graph with caching, it should be the same as the
value we would obtain by evaluating the expression directly. Second, the evaluation of previews 
using dependency graphs should -- in some cases -- reuse previously evaluated partial results.
In other words, this section shows that our mechanism is both correct and implements a useful 
optimization.

\subsection{Host language}
The method in this paper does not rely on the particulars of how the underlying programming 
language works. For this reason, we do not give a concrete definition of how member access
$e.m(e_1,\ldots, e_n)$ reduces to a value.

@@

[Rightsquigarrow allows beta anywhere? then it works...]

@@

\item 
Compositionality, i.e. if $e \rightsquigarrow e'$ and $C[e] \rightsquigarrow e''$ then also
  $C[e'] \rightsquigarrow e''$.

\item
Extensionality -- if $C1[e1] \rightsquigarrow e$ and $C1[e2] \rightsquigarrow e$ then $C2[fn e1] \rightsquigarrow ee$ and $C2[fn e2] \rightsquigarrow ee$

\end{itemize}
\end{definition}

@@

First is corrctness (Theorem~\ref{thm:correcntess}) -- no matter how a graph is constructed, when 
we use it to evaluate a preview for an expression, the preview is the same as the value we would 
obtain by evaluating the expression directly. Second is determinacy (Theorem~\ref{thm:determinacy}) --
if we cache a preview for a graph node and update the graph, the preview would still be the same
when evaluated using an updated graph.

This is the correctness and determinacy property discussed in Section~\ref{sec:properties-correct}.

@@

xxx

\begin{theorem}[Determinacy]
\label{thm:determinacy}
Downarrow will always evaluate the same, if we add things to a graph in the defined way.
(this means that we can cache)
\end{theorem}

~

~

~

[Only dependency graph matters, not the history and symbols]
[Symbols are effectively hashes of dependencies]

\begin{lemma}
\label{thm:lemma-lookup}
Lemma X - lookup with red mem(m) returns blue mem(m, s)
\end{lemma}

\begin{theorem}[Let-free correctness]
Given an expression $e$ that has no free variables and does not contain let bindings, together
with a lookup table $\Delta$ obtained from any sequence of expressions according to Figure~\ref{fig:loop}
let $\bndclr{v}, (V, E) = \ident{bind}_{\emptyset, \Delta}(e)$. If $\bndclr{v}\Downarrow d$ 
over a graph $(V, E)$ then $d = p$ for some $p$ and $e \rightsquigarrow p$.
\end{theorem}
\begin{proof}
First note that, when combining recursively constructed sub-graphs, the \ident{bind} operation
adds new nodes and edges leading from those new nodes. Therefore, an evaluation using $\Downarrow$
over a sub-graph will also be valid over the new graph.

Next, we prove a more general property using induction showing that for $e$ such 
that $\bndclr{v}, (V, E) = \ident{bind}_{\emptyset, \Delta}(e)$:
\begin{enumerate}
\item[a.] If $FV(e)=\emptyset$ then $\bndclr{v} \Downarrow p$ for some $p$ and $e \rightsquigarrow p$
\item[b.] Otherwise, $\bndclr{v} \Downarrow \llbracket e_p \rrbracket_{FV(e)}$ for some $e_p$ and
  for any evaluation context $C[-]$ such that $FV(C[e_p])=\emptyset$ it holds that if
  $C[e_p] \rightsquigarrow v$ for some $v$ then $C[e] \rightsquigarrow v$.  
\end{enumerate}
The proof is done by induction over the binding process, which follows the structure 
of the expression $e$ and can be found in Appendix~\ref{sec:app-correctness}.
\end{proof}

\begin{theorem}[Correctness]
\label{thm:correctness}
(Same as let-free version, but using let elimination to say that this works for any expression)
\end{theorem}

@@

\appendix 
\section{Appendix}
\label{sec:app-correctness}
\begin{theorem}[Let-free correctness]
Given an expression $e$ that has no free variables and does not contain let bindings, together
with a lookup table $\Delta$ obtained from any sequence of expressions according to Figure~\ref{fig:loop}
let $\bndclr{v}, (V, E) = \ident{bind}_{\emptyset, \Delta}(e)$. If $\bndclr{v}\Downarrow d$ 
over a graph $(V, E)$ then $d = p$ for some $p$ and $e \rightsquigarrow p$.
\end{theorem}
\begin{proof}
First note that, when combining recursively constructed sub-graphs, the \ident{bind} operation
adds new nodes and edges leading from those new nodes. Therefore, an evaluation using $\Downarrow$
over a sub-graph will also be valid over the new graph.

Next, we prove a more general property using induction showing that for $e$ such 
that $\bndclr{v}, (V, E) = \ident{bind}_{\emptyset, \Delta}(e)$:
\begin{enumerate}
\item[a.] If $FV(e)=\emptyset$ then $\bndclr{v} \Downarrow p$ for some $p$ and $e \rightsquigarrow p$
\item[b.] Otherwise, $\bndclr{v} \Downarrow \llbracket e_p \rrbracket_{FV(e)}$ for some $e_p$ and
  for any evaluation context $C[-]$ such that $FV(C[e_p])=\emptyset$ it holds that if
  $C[e_p] \rightsquigarrow v$ for some $v$ then $C[e] \rightsquigarrow v$.  
\end{enumerate}

The proof is done by induction over the binding process, which follows the structure 
of the expression $e$:

\vspace{0.75em}\noindent(1) $\ident{bind}_{\Gamma, \Delta}(e_0.m(e_1, \ldots, e_n))$ -- 
  Here $e = e_0.m(e_1, \ldots, e_n)$, $\bndclr{v_i}$ are graph nodes obtained by induction for
  expressions $e_i$ and $\{ (\bndclr{v}, \bndclr{v_0}, \blbl{arg}(0)), \ldots, (\bndclr{v}, \bndclr{v_n}, \blbl{arg}(n))\} \subseteq E$
  From Lemma~\ref{thm:lemma-lookup}, $\bndclr{v} = \bnd{mem}(m, s)$ for some $s$.

  If $FV(e)=\emptyset$, then $\bndclr{v_i} \Downarrow p_i$ for $i\in 0\ldots n$ and   
  $\bndclr{v}\Downarrow p$ using (\emph{mem-val}) such that $p_0.m(p_1, \ldots, p_n) \rightsquigarrow p$. 
  From induction hypothesis, $e_i \rightsquigarrow p_i$ and so, using compositionality of $\rightsquigarrow$, 
  $e_0.m(e_1, \ldots, e_n) \rightsquigarrow p$.

  If $FV(e)\neq\emptyset$, then $\bnclr{v_i} \Downarrow_\ident{lift} \llbracket e'_i \rrbracket$ for $i\in 0\ldots n$ and 
  $\bndclr{v}\Downarrow \llbracket e'_0.m(e'_1, \ldots, e'_n) \rrbracket_{FV(e)}$ using (\emph{mem-expr}).
  From induction hypothesis, for any $C[-]$, if $C[e'_i] \rightsquigarrow v_i$ then $C[e_i] \rightsquigarrow v_i$.
  Using compositionality, it also holds that for any $C[-]$, if $C[e'_0.m(e'_1, \ldots, e'_n)]\rightsquigarrow v$
  then also $C[e_0.m(e_1, \ldots, e_n)] \rightsquigarrow v$.

\vspace{0.75em}\noindent(2) $\ident{bind}_{\Gamma, \Delta}(e_0.m(e_1, \ldots, e_n))$ --
  This case is similar to (1), except that the fact that $\bndclr{v} = \bnd{mem}(m, s)$
  holds by construction, rather than using Lemma~\ref{thm:lemma-lookup}.

\vspace{0.75em}\noindent(3) We assume that the expression $e$ does not include let bindings and
  so this case never happens.

\vspace{0.75em}\noindent(4) $\ident{bind}_{\Gamma, \Delta}(n)$ -- In this case $e=n$ and $\bndclr{v} = \bnd{val}(n)$. The preview of
  $\bnd{val}(n)$ is evaluated to $n$ using the (\emph{val}) case.

\vspace{0.75em}\noindent(5) $\ident{bind}_{\Gamma, \Delta}(x)$ -- The initial $\Gamma$ is empty and
  there are no let bindings, so $x$ must have been added to $\Gamma$ by case (6) or (7). Hence,
  $\bndclr{v}=\bnd{var}(x)$. Using (\emph{var}) $\bndclr{v}\Downarrow \llbracket x \rrbracket_{x}$
  and so $e_p = e = x$ and the second case (b.) trivially holds.

\vspace{0.75em}\noindent(6) $\ident{bind}_{\Gamma, \Delta}(\lambda x\rightarrow e)$ -- Assume
  $\bndclr{v_b}$ is a graph node representing the body. The evaluation can use one of three rules:

  If $FV(e)=\emptyset$ then $\bndclr{v_b}\Downarrow p_b$ for some $p_b$ and $\bndclr{v}\Downarrow \lambda x.p_b$ 
  using (\emph{fun-val}). From induction $e_b \rightsquigarrow p_b$
  and so, using extensionality of $\rightsquigarrow$ also $\lambda x.e_b \rightsquigarrow \lambda x.p_b$.

  If $FV(e)=\{x\}$ then $\bndclr{v_b}\Downarrow \llbracket e_b \rrbracket_x$ for some $e_b$ and
  $\bndclr{v}\Downarrow \lambda x.e_b$ using (\emph{fun-bind}). From 
  induction, for any $C[-]$, if $C[e_b] \rightsquigarrow v$ then also $C[e] \rightsquigarrow v$.
  By extensionality, using an empty context $C[-]=-$ it holds that if $\lambda x.e \rightsquigarrow \lambda x.e_b$.

  Otherwise, $\bndclr{v_b}\Downarrow \llbracket e_b \rrbracket_{x,\Gamma}$ for some $e_b$ and
  $\bndclr{v}\Downarrow \llbracket\lambda x.e_b\rrbracket_\Gamma$ using (\emph{fun-expr}). From
  induction, for any $C[-]$, if $C[e_b] \rightsquigarrow v$ then also $C[e] \rightsquigarrow v$.
  By extensionality, if $C'[\lambda x.e_b] \rightsquigarrow v$ then also
  $C'[\lambda x.e] \rightsquigarrow v$.
\end{proof}
